The role of emotional factors in face processing abilities in Autism Spectrum Conditions

### 2023-07-17 manuscript.Rmd
Fixed the Mann-Whitney issue in Table 9

emotas <- by(data$HANX7,data$TAS_Group,summary)
groupcount <- table(data$TAS_Group)
mwu <- wilcox.test(HANX7 ~ TAS_Group, data = data)
mwz <- capture.output(wilcox_test(data$HANX7 ~ as.factor(data$TAS_Group)))
mwz2 <- strsplit(gsub("([*]+$)|[<]", "", mwz[5]), "\\s+")
table9data[8,2] <- round(unlist(emotas[[2]])[3],digits=4)
table9data[8,3] <- groupcount[2]
table9data[8,4] <- round(unlist(emotas[[1]])[3],digits=4)
table9data[8,5] <- groupcount[1]
table9data[8,6] <- paste0(mwu$statistic, ', ', mwz2[[1]][3],' ', p_format(mwu$p.value,digits=3,leading.zero=F,accuracy=0.001))

>>>>

emotas <- by(data$HANX7,data$TAS_Group,summary)
groupcount <- table(data$TAS_Group)
mwu <- wilcox.test(data$HANX7[which(data$TAS_Group==1)],data$HANX7[which(data$TAS_Group==0)])
mwz <- capture.output(wilcox_test(data$HANX7 ~ as.factor(data$TAS_Group)))
mwz2 <- strsplit(gsub("([*]+$)|[<]", "", mwz[5]), "\\s+")
table9data[8,2] <- round(unlist(emotas[[2]])[3],digits=4)
table9data[8,3] <- groupcount[2]
table9data[8,4] <- round(unlist(emotas[[1]])[3],digits=4)
table9data[8,5] <- groupcount[1]
table9data[8,6] <- paste0(mwu$statistic, ', ', mwz2[[1]][3],' ', p_format(mwu$p.value,digits=3,leading.zero=F,accuracy=0.001))

### 2023-07-17 manuscript.tex
Fixed the Mann-Whitney issue in Table 9

\caption{\label{tab:table9}Comparing face processing variables, autistic traits and anxiety and depression symptoms between high and low alexithymia groups.}
\centering
\begin{tabular}[t]{lrrrrl}
\toprule
 & High Alexithymia &  & Low Alexithymia &  & Mann Whitney U, Z,\\
 & Group (Mdn) & N & Group (Mdn) & N & p-value (two-sided)\\
\midrule
Emotion Attribution & 0.1588 & 63 & 0.1411 & 111 & 3082, -1.298, .195\\
Identity Attribution & 0.1 & 63 & 0.0958 & 107 & 3052.5, -1.026, .306\\
Emotion PSE & 0.497 & 63 & 0.4927 & 111 & 3151.5, -1.0803, .281\\
\addlinespace
Identity PSE & 0.5284 & 65 & 0.5287 & 111 & 3348, -0.79548, .427\\
AQ & 88 & 65 & 67 & 113 & 1390.5, -6.897, <.001\\
HADS Anxiety & 9 & 65 & 11 & 113 & 4811.5, 3.4607, <.001\\
HADS Depression & 9 & 65 & 9 & 113 & 3163.5, -1.5557, .12\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:table9}Comparing face processing variables, autistic traits and anxiety and depression symptoms between high and low alexithymia groups.}
\centering
\begin{tabular}[t]{lrrrrl}
\toprule
 & High Alexithymia &  & Low Alexithymia &  & Mann Whitney U, Z,\\
 & Group (Mdn) & N & Group (Mdn) & N & p-value (two-sided)\\
\midrule
Emotion Attribution & 0.1588 & 63 & 0.1411 & 111 & 3082, -1.298, .195\\
Identity Attribution & 0.1 & 63 & 0.0958 & 107 & 3052.5, -1.026, .306\\
Emotion PSE & 0.497 & 63 & 0.4927 & 111 & 3151.5, -1.0803, .281\\
\addlinespace
Identity PSE & 0.5284 & 65 & 0.5287 & 111 & 3348, -0.79548, .427\\
AQ & 88 & 65 & 67 & 113 & 1390.5, -6.897, <.001\\
HADS Anxiety & 9 & 65 & 11 & 113 & 2533.5, 3.4607, <.001\\
HADS Depression & 9 & 65 & 9 & 113 & 3163.5, -1.5557, .12\\
\bottomrule
\end{tabular}
\end{table}
